model_white

### 2024-03-16 models/model_black.Rmd
Model validation, comparision

>>>>

```{r}
# Leave-One-Out Cross-Validation (LOO) for model comparison
loo_neg_binom_black <- loo(neg_binom_model)
loo_poisson_black <- loo(poisson_model)
loo_comparison_black <- loo_compare(loo_neg_binom_black, loo_poisson_black)
print(loo_comparison_black)
```

```{r}
# Posterior Predictive Checks
# Posterior predictive check for the Negative Binomial model
pp_check_neg_binom_black <-
  pp_check(neg_binom_model)  + ggtitle("Negative Binomial Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_neg_binom_black.png",
  plot = pp_check_neg_binom_black,
  width = 10,
  height = 8
)
pp_check_neg_binom_black

# Posterior predictive check for the Poisson model
pp_check_poisson_black <-
  pp_check(poisson_model)  + ggtitle("Poisson Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_poisson_black.png",
  plot = pp_check_poisson_black,
  width = 10,
  height = 8
)
pp_check_poisson_black
```

### 2024-03-16 models/model_hispanic.Rmd
moving files
moved the model files to the appropriate folder.
Model validation, comparision

---
title: "model_notstated"
format: html
---

@@

# Filter for the year 2014 and the specific race
race_name <- "Not Stated/Unknown"

@@

>>>>

---
title: "model_hispanic"
format: html
---

@@

# Filter for the year 2014 and the specific race
race_name <- "Hispanic"

@@

```{r}
# Leave-One-Out Cross-Validation (LOO) for model comparison
loo_neg_binom_hispanic <- loo(neg_binom_model)
loo_poisson_hispanic <- loo(poisson_model)
loo_comparison_hispanic <- loo_compare(loo_neg_binom_hispanic, loo_poisson_hispanic)
print(loo_comparison_hispanic)
```

```{r}
# Posterior Predictive Checks
# Posterior predictive check for the Negative Binomial model
pp_check_neg_binom_hispanic <-
  pp_check(neg_binom_model)  + ggtitle("Negative Binomial Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_neg_binom_hispanic.png",
  plot = pp_check_neg_binom_hispanic,
  width = 10,
  height = 8
)
pp_check_neg_binom_hispanic

# Posterior predictive check for the Poisson model
pp_check_poisson_hispanic <-
  pp_check(poisson_model)  + ggtitle("Poisson Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_poisson_hispanic.png",
  plot = pp_check_poisson_hispanic,
  width = 10,
  height = 8
)
pp_check_poisson_hispanic
```

### 2024-03-16 models/model_notstated.Rmd
Model validation, comparision

>>>>

```{r}
# Leave-One-Out Cross-Validation (LOO) for model comparison
loo_neg_binom_notstated <- loo(neg_binom_model)
loo_poisson_notstated <- loo(poisson_model)
loo_comparison_notstated <- loo_compare(loo_neg_binom_notstated, loo_poisson_notstated)
print(loo_comparison_notstated)
```

```{r}
# Posterior Predictive Checks
# Posterior predictive check for the Negative Binomial model
pp_check_neg_binom_notstated <-
  pp_check(neg_binom_model)  + ggtitle("Negative Binomial Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_neg_binom_notstated.png",
  plot = pp_check_neg_binom_notstated,
  width = 10,
  height = 8
)
pp_check_neg_binom_notstated

# Posterior predictive check for the Poisson model
pp_check_poisson_notstated <-
  pp_check(poisson_model)  + ggtitle("Poisson Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_poisson_notstated.png",
  plot = pp_check_poisson_notstated,
  width = 10,
  height = 8
)
pp_check_poisson_notstated
```

### 2024-03-16 models/model_white.Rmd
moving files
moved the model files to the appropriate folder.
Model validation, comparision

---
title: "model_other"
format: html
---

@@

# Filter for the year 2014 and the specific race
race_name <- "Other Race/Ethnicity"

@@

>>>>

---
title: "model_white"
format: html
---

@@

# Filter for the year 2014 and the specific race
race_name <- "White Non-Hispanic"

@@

```{r}
# Leave-One-Out Cross-Validation (LOO) for model comparison
loo_neg_binom_white <- loo(neg_binom_model)
loo_poisson_white <- loo(poisson_model)
loo_comparison_white <- loo_compare(loo_neg_binom_white, loo_poisson_white)
print(loo_comparison_white)
```

```{r}
# Posterior Predictive Checks
# Posterior predictive check for the Negative Binomial model
pp_check_neg_binom_white <-
  pp_check(neg_binom_model)  + ggtitle("Negative Binomial Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_neg_binom_white.png",
  plot = pp_check_neg_binom_white,
  width = 10,
  height = 8
)
pp_check_neg_binom_white

# Posterior predictive check for the Poisson model
pp_check_poisson_white <-
  pp_check(poisson_model)  + ggtitle("Poisson Model")
ggsave(
  "../data/analysis_data/Model_Output/pp_check_poisson_white.png",
  plot = pp_check_poisson_white,
  width = 10,
  height = 8
)
pp_check_poisson_white
```
